XXX

### 2012-03-25 paper/engNERwiki.tex
Fixed the botched merging.

@@

As of version 3.7, the DBpedia ontology allows multiple superclasses, making the hierarchy a directed acyclic graph\footnote{http://blog.dbpedia.org/2011/09/11/dbpedia-37-released-including-15-localized-editions}. This introduces the problem of selecting the right superclass, and hence, CoNLL mapping for classes with more than one parent. In version 3.7, the only such class is \texttt{Library}, which can be traced back to both \texttt{Place} and \texttt{Organisation}.

@@

% The full mapping can be found in Appendix~\ref{sec:appa}.
%
Using the mapping described above, we compile an entity list that contains all entities in DBpedia tagged with the appropriate CoNLL named entity category.

@@

There is another special case in Hungarian: opposite to English, the number of compund words is quite large, and NEs can also be subjects of compounding. In this case the common noun following the NE is joint with a hyphen, so they constitute one token. However, the joint common noun can modify the original sense of NE, depending on the semantics of the common noun. For example: in the compound \textit{SAP-szoftvercég} ['SAP software company'] the common noun does not change the labeling, but in the case of the compound \textit{WorldCom-botrány} ['WorldCom scandal'] the NE tag changes from ORG to O.

@@

The corpora are released under the Creative Commons Attribution-Sharealike 3.0 Unported License (CC-BY-SA), the same license under which the text of Wikipedia is released. The data files can be freely downloaded from ...\footnote{To be filled in in the camera-ready version.}.

The corpora are available in multitag format. Content lines are tab separated; there is one column for the tokens plus one column per tagset. Sentence boundaries are marked by empty lines. The linguistic features include the lemmatized form of the word and its part-of-speech tag. Two NE tags are included with each word: one is the most specific DBpedia category it belongs to, if any; the other is the CoNLL NE tag. While the NE tags can be considered as a "silver standard", the linguistic features are provided on a "best-effort" basis.

@@

% Corpus sizes, performance, tagging conventions
% Hun -> not utf-8, loss of precision?
%measuring Wikipedia's inconsistency using n-gram tag variation (\cite{Nothman:09})
%ez jó mérőszám lehet a gold standard korpuszok összehasonlítására
%használhatjuk fordítva is: ha egy adott nucleus ugyanolyan n-gram környezetben nagyon sokszor van X-ként taggelve, és kevésszer Y-ként, akkor az Y-okat is átcsinálhatnánk X-szé

>>>>

Supervised Named Entity Recogizers require large amount of annotated texts. However, manual annotation is a highly costly procedure, thus reducing the annotation cost is essential. We present a fully automatic method to build NE-annotated corpora from Wikipedia. In contrast to recent work, we apply a new method, which maps the DBpedia classes into CoNLL NE types. Since our method is mainly language-independent, we used it for generating corpora for English and Hungarian, as well. The corpora are freely available.

@@

As of version 3.7, the DBpedia ontology allows multiple superclasses, making the hierarchy a directed acyclic graph\footnote{http://blog.dbpedia.org/2011/09/11/dbpedia-37-released-including-15-localized-editions}. This introduces the problem of selecting the right superclass, and hence, CoNLL mapping for classes with more than one parent. In version 3.7, the only such class is \textit{Library}, which can be traced back to both \textit{Place} and \textit{Organisation}.

@@

%The full mapping can be found in Appendix~\ref{sec:appa}.

Using the mapping described above, we compile an entity list that contains all entities in DBpedia tagged with the appropriate CoNLL named entity category.

@@

There is another special case in Hungarian: opposite to English, the number of compund words is quite large and NEs can also be subjects of compounding. In this case the common noun following the NE is joint with a hyphen, so they constitute one token. However, the joint common noun can modify the original sense of NE, depending on the semantics of the common noun. For example: in the compound \textit{SAP-szoftvercég} ['SAP software company'] the common noun does not change the labeling, but in the case of the compound \textit{WorldCom-botrány} ['WorldCom scandal'] the NE tag changes from ORG to O.

@@

The corpora are available under the Creative Commons Attribution-Sharealike 3.0 Unported License (CC-BY-SA), the same license under which the text of Wikipedia is released. The data files can be freely downloaded from ...\footnote{To be filled in in the camera-ready version.}.

The files are in multitag format. Content lines are tab separated; there is one column for the tokens plus one column per tagset. Sentence boundaries are marked by empty lines. The linguistic features include the lemmatized form of the word and its part-of-speech tag. Two NE tags are included with each word: one is the most specific DBpedia category it belongs to, if any; the other is the CoNLL NE tag. While the NE tags can be considered as a "silver standard", the linguistic features are provided on a "best-effort" basis.

@@
